Supplementary Materials for: Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints

### 2023-10-20 supp/supp.qmd
Adding fig to supplement rather than main MS

>>>>

# Supplementary Results

```{r, figdates}
#| label: fig-figdates
#| fig-cap: Number of preprints published monthly to *EcoEvoRxiv* between 2018 and 2023.

ggplot(data, aes(x = `Published Date`)) +
  geom_histogram(fill = "grey", color = "black") +
  labs(x = "Published Date", y = "Number of preprints") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
